diffusion, websites with 1 pc

### 2023-03-22 src/level_lisa_la.Rmd
error
lisa maps

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

@@

@@

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
                                     }

>>>>

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per firm in a LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}

@@

```{r, eval=F}

@@

map <- tm_shape(mun_merge_new, projection = "+init=epsg:4326") + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per firm in a LA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(la, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ") +
tmap_options(check.and.fix = TRUE)
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
                                     }

### 2023-03-22 src/level_lisa_oa.Rmd
lisa maps

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant", "High-High","Low-Low","Low-High","High-Low"), 
                                         title="LISA for level, OA") +
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(gb, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

@@

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

r2.all <- dens.London %>% 
  rename(London = rsquared)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

>>>>

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per OA") + 
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(gb, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

@@

```{r, eval = F}

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

r2.all <- dens.London %>% 
  rename(London = rsquared)

# Help for OA area size. I double checked the largest: E00102963
# It is correct, this is its size.
# ggplot(df, aes(x=area)) +
#     geom_histogram(binwidth=.5, colour="black", fill="white")
# 
# df %>% filter(area>50)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)
